Visually pleasing knot projections

### 2021-09-26 inst/jma_rebuttal.tex

\textcolor{blue}{Only the first six lines are shown for brevity, I have
  changed the text accordingly: ``Above we see only the first six lines
of the object"}

Figure 3: What is the color assignment? - one color for each Bezier
segment?  How many circles are drawn for each segment?  (Say that
solid blotches result from densely overlapping circles.)

\textcolor{blue}{The original caption was lacking detail.
  \begin{description}
  \item[OLD text] ``The \emph{path} of (unoptimized) knot~$7_6$,
    showing Bezier handles as thin straight lines and circles.  The
    coloured circles have a radius proportional to the curvature (that
    is, the reciprocal of the radius of curvature) along the strand;
    note large curvature at loop on left"
  \item[NEW text] ``The \emph{path} of (unoptimized) knot~$7_6$,
    showing Bezier handles as thin straight lines and circles.  The
    coloured circles have a radius proportional to the curvature (that
    is, the reciprocal of the radius of curvature) along the strand.
    Colouring is arbitrary, one color for each Bezier segment; solid
    blotches result from densely overlapping circles.  Note large
    curvature at loop on left"
  \end{description}
  Each segment has one circle per control point (which defaults to
  $n=100$) but this is user-settable.
}

Figure 4: Why is this required?  -- Does the user have to specify the
type of crossing via an "overunder" object?  -- (Lines 53-62?)%issue28

\textcolor{blue}{The {\tt overunderobject} specifies which of two
  strands at a crossing is the overstrand and which the understand.  I
  have added a definition of this and a brief discussion in the figure
  caption.}

@@

Fig. 10: Why is the absence of mirror symmetry pointed out here?

Fig. 11: Why is this table shown?  It is not mentioned in the main
text.  The figures are ``better" than in Figure 1, but still not
optimal in the spirit of this paper.  ``Rolfsen" needs a reference.

%issue32

\textcolor{blue}{Rolfsen now cited, and a discussion of the table now
  given to place it in context.}

@@

\section*{Detailed rebuttal: Reviewer \#2}

This lovely article addresses the interesting question of
how to produce pleasing and informative images of two dimensional knot
diagrams. In addition to the discussion it describes how to use a
combination of the software packages Inkscape and R to optimise knots.

At the moment, however the paper is a little too close to simply being
a software manual for the software, and needs in particular to
describe the techniques used by the software to create the optimised
images.

In addition there is a rather consistent use of absolute terms for
pleasing vs ugly knots. Aesthetics is a complex field, but generally
does not provide strong answers.

\textcolor{blue}{Absolute terms now rephrased more carefully.}%issue#36

While the choices made in this paper
are reasonable, they are simply stated, rather than including a
justification for why they are chosen. They certainly only apply to a
particular knid of knot diagram. This can be see in the final image
showing all the knots with up to 8 crossings. While some of the
resulting diagrams are beautiful, I particularly enjoyed {\tt 8\_10}
and {\tt 8\_17}, some are not so pleasing to me. In particular the
algorithm given likes to over-tighten when the line wraps round
itself. This can be seen particularly in {\tt 8\_3}, but also in {\tt
  8\_5}, {\tt 8\_6} and {\tt 8\_11}. This is itself a personal
preference not an absolute, but a discussion of how to adjust the
set-up of the software to make personal aesthetic choices would
strengthen the paper.

### 2021-09-26 inst/jma_knot.tex
fixes #28

\begin{figure}[!tbp]
\begin{verbatim}
knotplot2(k7_6,text=TRUE,lwd=1,circ=0,rainbow=TRUE)
\end{verbatim}
 \centering
\includegraphics[scale = 0.9]{knot-004}
\caption{Knot~$7_6$ with strands numbered \label{k76_strands} to guide
creation of over and under information} \end{figure}

>>>>

\begin{figure}[!tbp]
\begin{verbatim}
knotplot2(k7_6,text=TRUE,lwd=1,circ=0,rainbow=TRUE)
\end{verbatim}
 \centering
\includegraphics[scale = 0.9]{knot-004}
\caption{Knot~$7_6$ with strands numbered \label{k76_strands} so that
  the sense of the crossings can be established.  For example, strand
  7 passes over strand 3.  In the package, this fact is specified by
  the {\tt overunder} object, as discussed in the text, having a row
  {\tt 7 3} (and not {\tt 3 7} which would be the crossing having the
  opposite sense)} \end{figure}
